---
title: "Meta-analysis AI algorithms against non-experts, experts, and scores"
author: "Luis A. Figueroa, Marcelo Montero, Alisson Samaniego, et. al."
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile),'/README.md')) })
output: github_document
---

```{r setup, include=FALSE}
library(tidyr)
library(dplyr)
library(rmarkdown)
library(metafor)
library(readxl)
library(forestplot)

knitr::opts_chunk$set(fig.path = "Figures/", dev='svg')

```

<i> Analysis and visualization developed by [Luis A. Figueroa](https://www.linkedin.com/in/luis-figueroa-200851374/) </i>

We built this project to show the meta-analysis AI algorithms (RWPT-II algorithm, Basel algorithm, WCT Formula, WCT Formula II, VT Prediction Model, Solo Model, Paired Model, VT score, Bayesian algorithm) against Gold Standard (Humans experts <electrophysiology>, humans non-experts <general>, and score algorithms) allowing transparency and reproducibility.



```{r functions_md&or, echo=FALSE, message=FALSE, warning=FALSE}
meta_auc <- function(database, effect = "CLES") {
  db <- database
  # Inicializar columnas
  db$yi <- NA
  db$vi <- NA
  db$source <- "NR"
  
  # Usar AUC-acc-sens-spec ajustados (es, es_lw, es_up) si están disponibles
  adj_idx <- which(!is.na(db$es) & !is.na(db$es_lw) & !is.na(db$es_up))
  if(length(adj_idx) > 0) {
    db$yi[adj_idx] <- log(db$es[adj_idx])
    db$vi[adj_idx] <- ((log(db$es_up[adj_idx]) - log(db$es_lw[adj_idx])) / (2 * qnorm(0.975)))^2
    db$source[adj_idx] <- "adjusted"
  }
  
  # Ordenar por tamaño del efecto
  db <- db[order(db$yi), ]
  
  # Realizar meta-análisis
  ma <- rma(yi = db$yi, vi = db$vi, measure = effect, data = db, method = 'REML')
  exp <- predict(ma, transf = exp)
  
  # Calcular pesos
  db$weights <- weights(ma)
  db$w <- paste(formatC(db$weights, format = 'f', digits = 1), '%')
  
  # Resultado del meta-análisis
  list(
    pre = db,
    ma = ma,
    exp = exp,
    effect_type = effect,
    effect_label = "CLES/AUC")
}

limits_es <- function(ma_result){
    df <- data.frame(
  es = c(rep(NA, 2), ma_result$pre$es, NA, ma_result$exp$pred, NA),
  lower = c(rep(NA, 2), ma_result$pre$es_lw, NA, ma_result$exp$ci.lb, NA),
  upper = c(rep(NA, 2), ma_result$pre$es_up, NA, ma_result$exp$ci.ub, NA)
    )
    return(df)
  }

table_graph <- function(ma_result, effect_label = "Effect size", nstudies = 2) {
  b <- data.frame(
    Author = c(paste0("Study"),NA,
      as.character(ma_result$pre$study),NA,
      paste("Overall", effect_label, "for", nstudies, "studies"),
      paste0(
        "(Tau^2 = ", formatC(ma_result$ma$tau2, digits = 2, format = "f"),
        ", df = ", ma_result$ma$k - ma_result$ma$p,
        ", p ", ifelse(
          ma_result$ma$QEp < 0.001,
          "< 0.001",
          paste0("= ", formatC(ma_result$ma$QEp, digits = 3, format = "f"))
        ),
        "; I^2 = ", formatC(ma_result$ma$I2, digits = 1, format = "f"), "%)"
      )
    ),
    
    Algorithm = c(paste0("AI Algorithm tested"),NA,
                  as.character(ma_result$pre$ai_algorithm_used), NA, NA, NA),
    
    Comparator = c(paste0("Reference Standard"),NA,
                   as.character(ma_result$pre$comparator), NA, NA, NA),
    
    Effect = c(paste(effect_label, "(95% CI)"),NA,
      paste0(
        formatC(ma_result$pre$es, format = "f", digits = 2),
        " (",
        formatC(ma_result$pre$es_lw, format = "f", digits = 2),
        "-",
        formatC(ma_result$pre$es_up, format = "f", digits = 2),
        ")"
      ),NA,
      paste0(
        formatC(ma_result$exp$pred, format = "f", digits = 2),
        " (",
        formatC(ma_result$exp$ci.lb, format = "f", digits = 2),
        "-",
        formatC(ma_result$exp$ci.ub, format = "f", digits = 2),
        ")"
      ),
      NA
    ),
    
    Weight = c(paste0("Weight(%)"), NA, ma_result$pre$w, NA, NA, NA),
    
    check.names = FALSE
  )
  
  return(b)
}

plot_dicho <- function(format_table_graph, sizes_box, subtotal1_summary, limits, 
                       xticks, xlog = FALSE, limit_x){
  plot_ma <- forestplot(format_table_graph,
             graph.pos = 4,
             zero = NA,
             limits,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes_box,
             line.margin = 2,
             is.summary = subtotal1_summary,
             align = c('l', 'l', 'l', 'c','c'),
             ci.vertices = TRUE,
             xticks = xticks,
             xlog=xlog,
             clip = limit_x,
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"))
  return(plot_ma)
  }

# Coupled forest plot for sensitivity and specificity.
# All study/model rows are retained, including those reporting only one measure.
plot_coupled_sens_spec <- function(db_sens1 = NULL, db_spec1 = NULL,
                                   db_sens2 = NULL, db_spec2 = NULL,
                                   db_sens3 = NULL, db_spec3 = NULL,
                                   group_labels = c("Group 1", "Group 2", "Group 3"),
                                   xlim = c(0, 1),
                                   xticks = c(0, 0.25, 0.50, 0.75, 1)) {
  key_cols <- c("study","total_patients","ai_algorithm_used","n_test","comparator")

  prepare_sens <- function(db) {
    if (is.null(db)) {return(NULL)}
    
    if (is.list(db) && !is.data.frame(db)) {valid_elements <- db[sapply(db,
        function(x) {is.data.frame(x) && nrow(x) > 0})]
      if (length(valid_elements) == 0) {return(NULL)}
      db <- dplyr::bind_rows(valid_elements)
      }
    if (!is.data.frame(db) || nrow(db) == 0) {return(NULL)}

    if (!"es" %in% names(db) || all(is.na(db$es))) {return(NULL)}

    db %>%
      dplyr::select(dplyr::all_of(key_cols), sens = es, sens_lw = es_lw,
                    sens_up = es_up)}

  prepare_spec <- function(db) {
    if (is.null(db)) {return(NULL)}

    if (is.list(db) && !is.data.frame(db)) {valid_elements <- db[sapply(db,
          function(x) {is.data.frame(x) && nrow(x) > 0})]

      if (length(valid_elements) == 0) {return(NULL)}
    db <- dplyr::bind_rows(valid_elements)}

    if (!is.data.frame(db) || nrow(db) == 0) {return(NULL)}

    if (!"es" %in% names(db) || all(is.na(db$es))) {return(NULL)}

    db %>%
      dplyr::select(dplyr::all_of(key_cols), spec = es, spec_lw = es_lw, 
                    spec_up = es_up)}

  combine_group <- function(db_sens, db_spec, group_name) {
    sens <- prepare_sens(db_sens)
    spec <- prepare_spec(db_spec)
  
    group_row <- data.frame(study = NA_character_, total_patients = NA_real_,
                            ai_algorithm_used = NA_character_, n_test = NA_real_,
                            comparator = group_name, sens = NA_real_, 
                            sens_lw = NA_real_, sens_up = NA_real_,
                            spec = NA_real_, spec_lw = NA_real_,
                            spec_up = NA_real_, stringsAsFactors = FALSE)

  if (is.null(sens) && is.null(spec)) {
    no_data_row <- data.frame(study = "-", total_patients = NA_real_, 
                              ai_algorithm_used = NA_character_, n_test = NA_real_,
                              comparator = NA_character_, sens = NA_real_,
                              sens_lw = NA_real_, sens_up = NA_real_,
                              spec = NA_real_, spec_lw = NA_real_, 
                              spec_up = NA_real_, stringsAsFactors = FALSE)
    return(dplyr::bind_rows(group_row, no_data_row))
  }


  if (is.null(sens)) {
    paired <- spec %>%
      dplyr::mutate(sens = NA_real_, sens_lw = NA_real_, sens_up = NA_real_)
  } else if (is.null(spec)) {
    paired <- sens %>%
      dplyr::mutate(spec = NA_real_,spec_lw = NA_real_, spec_up = NA_real_)
  } else {
    paired <- dplyr::full_join(sens, spec, by = key_cols)
  }

  dplyr::bind_rows(group_row, paired)
  }

  paired1 <- combine_group(db_sens1, db_spec1, group_labels[1])
  paired2 <- combine_group(db_sens2, db_spec2, group_labels[2])
  paired3 <- combine_group(db_sens3, db_spec3, group_labels[3])
  paired <- dplyr::bind_rows(paired1, paired2, paired3)

  format_ci <- function(est, low, up) {
    ifelse(is.na(est) | is.na(low) | is.na(up), "-",
           sprintf("%.2f (%.2f–%.2f)", est, low, up))
    }

  sens_mean <- c(NA, paired$sens)
  sens_lower <- c(NA,paired$sens_lw)
  sens_upper <- c(NA,paired$sens_up)
  spec_mean <- c(NA,paired$spec)
  spec_lower <- c(NA,paired$spec_lw)
  spec_upper <- c(NA,paired$spec_up)
  is_summary <- c(TRUE, 
                  TRUE, rep(FALSE, nrow(paired1)-1),
                  TRUE, rep(FALSE, nrow(paired2)-1),
                  TRUE, rep(FALSE, nrow(paired3)-1))

  sens_table <- cbind(
    c("Study", as.character(paired$study)),
    c("AI algorithm used", as.character(paired$ai_algorithm_used)),
    c("Reference standard", ifelse(is.na(paired$comparator), "—", 
                                   as.character(paired$comparator))),
    c("Sensitivity (95% CI)", format_ci(paired$sens, paired$sens_lw, paired$sens_up))
  )

  spec_table <- cbind(
    c("Specificity (95% CI)",
      format_ci(paired$spec, paired$spec_lw, paired$spec_up)))
  
  sizes_st <- c(NA, rep(0.25, nrow(paired)))
  
  if (any(is.finite(paired$sens))) {
    fp_sens <- forestplot::forestplot(
      labeltext = sens_table,
      mean = sens_mean,
      lower = sens_lower,
      upper = sens_upper,
      is.summary = is_summary,
      hrzl_lines = list("2" = gpar (lwd=1, columns=1:5, col="black")),
      graph.pos = 5,
      zero = NA,
      xlog = FALSE,
      clip = xlim,
      xticks = xticks,
      boxsize=sizes_st,
      xlab = "Sensitivity",
      ci.vertices = TRUE,
      lineheight = grid::unit(0.7, "cm"),
      colgap = grid::unit(4, "mm"),
      graphwidth = grid::unit(6, "cm"),
      txt_gp = forestplot::fpTxtGp(label = grid::gpar(cex = 0.80),
                                   ticks = grid::gpar(cex = 0.80),
                                   xlab = grid::gpar(cex = 0.90),
                                   summary = grid::gpar(cex = 0.90)),
      col = forestplot::fpColors(box = "black",line = "black",summary = "black"))
  } else {
    fp_sens <- NULL
  }

  if (any(is.finite(paired$spec))) {
    fp_spec <- forestplot::forestplot(
      labeltext = spec_table,
      mean = spec_mean,
      lower = spec_lower,
      upper = spec_upper,
      is.summary = is_summary,
      graph.pos = 2,
      hrzl_lines = list("2" = gpar (lwd=1, columns=1:2, col="black")),
      zero = NA,
      xlog = FALSE,
      clip = xlim,
      boxsize=sizes_st,
      xticks = xticks,
      xlab = "Specificity",
      ci.vertices = TRUE,
      lineheight = grid::unit(0.7, "cm"),
      colgap = grid::unit(4, "mm"),
      graphwidth = grid::unit(6, "cm"),
      txt_gp = forestplot::fpTxtGp(label = grid::gpar(cex = 0.80),
                                   ticks = grid::gpar(cex = 0.80),
                                   xlab = grid::gpar(cex = 0.90),
                                   summary = grid::gpar(cex = 0.90)),
      col = forestplot::fpColors(box = "black",line = "black",summary = "black"))
    } else {
      fp_spec <- NULL}

  grid::grid.newpage()
  layout <- grid::grid.layout(nrow = 1, ncol = 2, 
                              widths = grid::unit(c(0.6, 0.22),"npc"))
  grid::pushViewport(grid::viewport(layout = layout))
  grid::pushViewport(grid::viewport(layout.pos.row = 1, layout.pos.col = 1))

  plot(fp_sens,new_page = FALSE)
  grid::popViewport()

  grid::pushViewport(grid::viewport(layout.pos.row = 1, layout.pos.col = 2))
  plot(fp_spec, new_page = FALSE)
  grid::popViewport()
  
  # Return data invisibly in case you want to inspect them
  invisible(paired)
}

```


```{r cleaning, include = FALSE}
raw_data <- read_excel("Dataset AI WCT AlgorithmsSS.xlsx")
names(raw_data) <- c("study", "id_study", "total_patients", "ai_algorithm_used", 
                     "model_architecture", "n_test", "paired_solo_model", "val_meth",
                     "ep_study_confirm", "comparator", "comparator_detailed",
                     "metrics", "auc", "lw_auc", "up_auc", "ppv", "lw_ppv", "up_ppv",
                     "npv", "lw_npv", "up_npv", "sens", "lw_sens", "up_sens",
                     "specif", "lw_specif", "up_specif", "acc", "lw_acc", 
                     "up_acc", "auc_valset", "acc_valset")
db <- raw_data %>% 
  select(-c(id_study, model_architecture, paired_solo_model, val_meth, ep_study_confirm,
            comparator_detailed, metrics, auc_valset, acc_valset)) %>%
  mutate(ai_algorithm_used = 
           ifelse(ai_algorithm_used == "VCG model\r\n", "VCG model",
           ifelse(ai_algorithm_used == "Random forest\r\n", "Random forest",
           ifelse(ai_algorithm_used == "\r\nSupport vector machine", "Support vector machine",
           ifelse(ai_algorithm_used == "CNN-based deep learning model using ZeroLess-DARTS neural architecture search", 'CNN using ZeroLess-DARTS search', ai_algorithm_used))))) %>%
    mutate(comparator = 
           ifelse(comparator == "EP study + IA", "EP study + AI", 
           ifelse(comparator == "EP cardiologists + EP study + IA", 
                  "EP cardiologists + EP study + AI",
           ifelse(comparator == "EP cardiologists + Non EP cardiologists + EP study +IA", 
                  "EP cardiologists + Non EP cardiologists + EP study +AI",
           ifelse(comparator == "EP cardiologists + EP study + IA",
                  "EP cardiologists + EP study + AI",
           ifelse(comparator == "EP cardiologists + Non EP cardiologists + EP study +IA",
                  "EP cardiologists + Non EP cardiologists + EP study +AI", 
                  comparator)))))) %>%
  mutate(across(c(study, ai_algorithm_used, comparator), as.factor)) %>%
  mutate(across(-c(study, ai_algorithm_used, comparator), as.numeric)) 

cols_general_info <- c("study", "total_patients", "ai_algorithm_used", 
                     "n_test", "comparator")
cols_format <- c("es", "es_lw", "es_up")

db_auc <- db %>%
  select(cols_general_info, auc, lw_auc, up_auc) %>%
  setNames(c(cols_general_info, cols_format)) %>%
  filter(if_all(all_of(cols_format[!is.na(cols_format)]), ~ !is.na(.)))

db_sens <- db %>%
  select(cols_general_info, sens, lw_sens, up_sens) %>%
  setNames(c(cols_general_info, cols_format)) %>% 
  filter(if_all(all_of(cols_format[!is.na(cols_format)]), ~ !is.na(.)))

db_spec <- db %>%
  select(cols_general_info, specif, lw_specif, up_specif) %>%
  setNames(c(cols_general_info, cols_format)) %>% 
  filter(if_all(all_of(cols_format[!is.na(cols_format)]), ~ !is.na(.)))

# db_acc <- db %>%
#   select(cols_general_info, acc, lw_acc, up_acc) %>%
#   setNames(c(cols_general_info, cols_format)) %>% 
#   filter(if_all(all_of(cols_format[!is.na(cols_format)]), ~ !is.na(.)))


### AUC
# EP-Cardiologist is only a part of, or all of gold standard
some_ep_cardio <- c("EP cardiologists", "EP cardiologists + EP study + AI",
                    "EP cardiologists + Non EP cardiologists", 
                    "EP cardiologists + Non EP cardiologists + EP study +AI")
db_auc_card <- filter(db_auc, comparator %in% some_ep_cardio)

# Only Non-EP
db_auc_non <- filter(db_auc, comparator == "Non-EP cardiologists")

# AI is only a part of, or all of gold standard
# EP study is or all of gold standard #!!! In this case is the same as the last
some_ai_std <- c("EP cardiologists + EP study + AI",
                 "EP cardiologists + Non EP cardiologists + EP study +AI",
                 "EP study + AI")
db_auc_ai <- filter(db_auc, comparator %in% some_ai_std)


# ### ACC
# # EP-Cardiologist is only a part of, or all of gold standard
# db_acc_card <- filter(db_acc, comparator %in% some_ep_cardio)
# 
# # Only Non-EP
# db_acc_non <- filter(db_acc, comparator == "Non-EP cardiologists")
# 
# # AI is only a part of, or all of gold standard
# # EP study is or all of gold standard #!!! In this case is the same as the last
# db_acc_ai <- filter(db_acc, comparator %in% some_ai_std)


### SENS
# EP-Cardiologist is only a part of, or all of gold standard #!!! there isn't
db_sens_card <- filter(db_sens, comparator %in% some_ep_cardio)

# Only Non-EP #!! no results
db_sens_non <- filter(db_sens, comparator == "Non-EP cardiologists")

# AI is only a part of, or all of gold standard
# EP study is or all of gold standard #!!! In this case is the same as the last
db_sens_ai <- filter(db_sens, comparator %in% some_ai_std)


### SPECIF
# EP-Cardiologist is only a part of, or all of gold standard
db_spec_card <- filter(db_spec, comparator %in% some_ep_cardio)

# Only Non-EP #!!! no results
db_spec_non <- filter(db_spec, comparator == "Non-EP cardiologists")

# AI is only a part of, or all of gold standard
# EP study is or all of gold standard #!!! In this case is the same as the last
db_spec_ai <- filter(db_spec, comparator %in% some_ai_std)


```

### METHODOLOGY

We conducted a meta-analysis focusing on performance metrics reported according to three different reference standards. AI algorithms were compared with electrophysiologists (EP), non-EP cardiologists, electrophysiologic studies, and other AI models. At least four studies provided sufficient information to calculate pooled effect sizes for each comparison.

Area under the receiver operating characteristic curve (AUC) values and their corresponding 95% confidence intervals were extracted from the included studies, and pooled estimates were obtained using random-effects models. Complete 2 × 2 diagnostic contingency tables (true positives [TP], false positives [FP], false negatives [FN], and true negatives [TN]) were not consistently reported; therefore, a hierarchical diagnostic test accuracy meta-analysis jointly modeling sensitivity and specificity could not be performed. When reported, sensitivity and specificity were synthesized separately using random-effects models and displayed both individually and in a coupled forest plot to facilitate study-level comparison. Sensitivity analyses were performed when multiple AI models were evaluated in the same study population.

Statistical analyses were performed using R 4.4.2 and RStudio. `metafor` and `forestplot` packages were used to perform the meta-analyses and generate graphical summaries.


### Forest plots

<details>
<summary> AUC for all reference standards </summary>

```{r auc_card, echo=FALSE, fig.height=7.5, fig.width=17, message=FALSE, warning=FALSE}
### SENSITIVE ANALYSIS
db_auc_card_s <- db_auc_card[c(1:2,4, 8,9),] # We prove per each model of Kashou, 2022
auc_card <- meta_auc(db_auc_card_s)
# print(auc_card)
auc_non <- meta_auc(db_auc_non)
db_auc_ai_s <- db_auc_ai[c(1:2,7,12),] # We prove per each model of Kashou, 2022
auc_ai <- meta_auc(db_auc_ai_s)
# print(auc_card)

subtotal1_card <- table_graph(auc_card,effect_label =  "AUC", nstudies = 5)
subtotal1_card[2,] <- c(NA,NA,"First group for at least one EP cardiologist", NA,NA)
subtotal1_non <- table_graph(auc_non, effect_label =  "AUC", nstudies = 1)
subtotal1_non <- subtotal1_non[-c(7,8),]
subtotal1_non[,5] <- NA
subtotal1_non[1,] <- NA
subtotal1_non[2,] <- c(NA,NA,"Second group for non-EP cardiologist, study nor AI", NA,NA)
subtotal1_ai <- table_graph(auc_ai, effect_label =  "AUC", nstudies = 4)
subtotal1_ai[1,] <- NA
subtotal1_ai[2,] <- c(NA,NA,"Third group for at leat one EP study or AI", NA,NA)
subtotal1 <- rbind(subtotal1_card, subtotal1_non, subtotal1_ai)
subtotal1 <- as.matrix(subtotal1)

sub_summary_card <- c(rep(T,2), rep(F, length(auc_card$pre$weights)), rep(T, 3))
sub_summary_non <- c(rep(T,2), rep(F, length(auc_non$pre$weights)), T) #rep(T, 3))
sub_summary_ai <- c(rep(T,2), rep(F, length(auc_ai$pre$weights)), rep(T, 3))
sub_summary <- append(sub_summary_card, c(sub_summary_non, sub_summary_ai))

sizes_dic_card <- c(rep(NA,2), 0.01*(auc_card$pre$weights), NA, 1, NA)
sizes_dic_non <- c(rep(NA,2), rep(0.5, length(auc_non$pre$weights)), NA)#, 1, NA)
sizes_dic_ai <- c(rep(NA,2), 0.01*(auc_ai$pre$weights), NA, 1, NA)
sizes_dic <- append(sizes_dic_card, c(sizes_dic_non, sizes_dic_ai))

subtotal1n_card <- limits_es(auc_card)
subtotal1n_non <- limits_es(auc_non)
subtotal1n_non <- subtotal1n_non[-c(7,8),]
subtotal1n_ai <- limits_es(auc_ai)
subtotal1n <- rbind(subtotal1n_card, subtotal1n_non, subtotal1n_ai)

xticks = c(0.8, 0.85, 0.9, 0.95,1)
limit_x = c(0.8,1)

plot_auc <- plot_dicho(format_table_graph = subtotal1, sizes_box = sizes_dic,
                       subtotal1_summary = sub_summary,
                        limits = subtotal1n, xticks = xticks, limit_x = limit_x, 
                        xlog = FALSE)

plot_auc
```

</details>


<details>
<summary> Coupled Forest Plot to show sensitivity and specificity </summary>

```{r coupled_sens_spec, echo=FALSE, fig.height=8, fig.width=20, message=FALSE, warning=FALSE}
sens_card <- meta_auc(db_sens_card)
sens_ai <- meta_auc(db_sens_ai)

spec_card <- meta_auc(db_spec_card)
spec_ai <- meta_auc(db_spec_ai)

plot_coupled_sens_spec(
  db_sens1 = sens_card,
  db_spec1 = spec_card,

  db_sens2 = NULL,
  db_spec2 = NULL,

  db_sens3 = sens_ai,
  db_spec3 = spec_ai,

  group_labels = c(
    "First group for at least one EP cardiologist",
    "Second group for non-EP cardiologist, study nor AI",
    "Third group for at leat one EP study or AI"
  )
)
```

</details>

ForestPlot separated:

<details>
<summary> Sensitivity for all reference standards </summary>

```{r sens_results, echo=FALSE, fig.height=5, fig.width=17, message=FALSE, warning=FALSE}
#one study for each measure
sens_card <- meta_auc(db_sens_card)
sens_ai <- meta_auc(db_sens_ai)

subtotal_card <- table_graph(sens_card, effect_label = "Sensitivity", nstudies = 1)
subtotal_card[2,] <- c(NA,NA,"First group for at least one EP cardiologist", NA,NA)
subtotal_ai <- table_graph(sens_ai, effect_label = "Sensitivity", nstudies = 8)
subtotal_ai[2,] <- c(NA,NA,"Third group for at leat one EP study or AI", NA,NA)
subtotal1 <- rbind(subtotal_card, subtotal_ai)
subtotal1[,5] <- NA
subtotal1 <- as.matrix(subtotal1[-c(5:7,18,19),])

sub_summary <- c(rep(T,2), rep(F, length(sens_card$pre$weights)), T, T,
                 rep(F, length(sens_ai$pre$weights)), T)

sizes_dic <- c(rep(NA,2), rep(0.35, length(sens_card$pre$weights)), NA, NA,
               rep(0.5, length(sens_ai$pre$weights)), NA)

subtotal1n_card <- limits_es(sens_card)
subtotal1n_ai <- limits_es(sens_ai)
subtotal1n <- rbind(subtotal1n_card, subtotal1n_ai)
subtotal1n <- as.matrix(subtotal1n[-c(5:7,18,19),])

xticks = c(0.6,0.7,0.8,0.9,1)
limit_x = c(0.6,1)
plot_sens <- plot_dicho(format_table_graph = subtotal1, sizes_box = sizes_dic,
                        subtotal1_summary = sub_summary,
                        limits = subtotal1n, xticks = xticks, limit_x = limit_x, 
                        xlog = TRUE)

plot_sens
```
</details>


<details>
<summary> Specificity for all reference standards </summary>

```{r spec_results, echo=FALSE, fig.height=5, fig.width=17, message=FALSE, warning=FALSE}
#one study for each measure
spec_card <- meta_auc(db_spec_card)
spec_ai <- meta_auc(db_spec_ai)

subtotal_card <- table_graph(spec_card, effect_label = "Specificity", nstudies = 1)
subtotal_card[2,] <- c(NA,NA,"First group for at least one EP cardiologist", NA,NA)
subtotal_ai <- table_graph(spec_ai, effect_label = "Specificity", nstudies = 8)
subtotal_ai[2,] <- c(NA,NA,"Third group for at leat one EP study or AI", NA,NA)
subtotal1 <- rbind(subtotal_card, subtotal_ai)
subtotal1[,5] <- NA
subtotal1 <- as.matrix(subtotal1[-c(5:7,18,19),])

sub_summary <- c(rep(T,2), rep(F, length(spec_card$pre$weights)), T, T,
                 rep(F, length(spec_ai$pre$weights)), T)

sizes_dic <- c(rep(NA,2), rep(0.35, length(spec_card$pre$weights)), NA, NA,
               rep(0.5, length(spec_ai$pre$weights)), NA)

subtotal1n_card <- limits_es(spec_card)
subtotal1n_ai <- limits_es(spec_ai)
subtotal1n <- rbind(subtotal1n_card, subtotal1n_ai)
subtotal1n <- as.matrix(subtotal1n[-c(5:7,18,19),])

xticks = c(0.6,0.7,0.8,0.9,1)
limit_x = c(0.6,1)

plot_spec <- plot_dicho(format_table_graph = subtotal1, sizes_box = sizes_dic,
                        subtotal1_summary = sub_summary,
                        limits = subtotal1n, xticks = xticks, limit_x = limit_x, 
                        xlog = TRUE)

plot_spec
```

</details>